New Exact Algorithms for Planar Maximum Covering Location by Ellipses Problems\tnoteref{t1}

### 2020-08-18 paper/article.tex
wip

\bibliographystyle{plainnat}

@@

		\title{New Exact Algorithms for Planar Maximum Covering Location by Ellipses Problems\tnoteref{t1}}
		\tnotetext[t1]{This paper is the results of the research
			project funded by CAPES and FAPESP.}

		\author[add1]{Danilo Tedeschi\corref{cor1}}
		\ead{danilo.tedeschi@usp.br}

@@

		\address[add1]{Department of Applied Mathematics and Statistics, Institute of Mathematical and Computer Sciences, University of São Paulo, Avenida Trabalhador São-carlense, 400, Centro, 13566-590, São Carlos, SP, Brazil.}

@@

\section{Conclusion}\label{section:conclusion}
\input{conclusion.tex}

>>>>

\bibliographystyle{elsarticle-template/model2-names}
%\biboptions{longnamesfirst,angle,semicolon}

@@

		\title{New Exact Algorithms for Planar Maximum Covering Location by Ellipses Problems\tnoteref{t1}}
	%	\tnotetext[t1]{This paper is the results of the research
	%		project funded by CAPES and FAPESP.}

		\author[add1]{Danilo Tedeschi\corref{cor1}}
		\ead{danilof.t2@gmail.com}

@@

		\address[add1]{Departamento de Matemática Aplicada e Estatística, Instituto de Ciências Matemáticas e de Computação, Universidade de São Paulo, Avenida Trabalhador São-carlense, 400, Centro, 13566-590, São Carlos, SP, Brazil.}

@@

\section{Conclusion}\label{section:conclusion}
\input{conclusion.tex}
{\color{Brown}
\section{Acknowledgments}\label{section:acknowledgements}
\input{acknowledgments.tex}
}
